\input cantar.sty
\zacatek{song\hskip 3.5cm\break\vskip-.6cm book}{of english songs}


\song{if}{}

if /e i was a /D minstrel i'd /e sing you six /h love songs
to /e tell how you're /h welcome to log /e cabin /h to /e share \S

if i was a merchant i'd bring you six diamonds
and six blowin roses for my love to wear

\R but /G i'm a /h simple man a /e poor common /C farmer
   so /e take my six /h roses to /e tie back /h your /e hand **

if i was the emperor i'd build you six palaces
with six hundred servants for comfort you'd have \S

if i was the emperor i'd build you six palaces
so take my six roses to tie back your hand

\r but...

%\bye


\Song{cottonfields back home}{}

when i was pretty little baby
my mamma would rock me in my craddle
in them old cotton fields back home \s

now, when them old fields get rotten
you can't pick very much cotton
in them old cotton fields back home
it was down in louisiana
just about a mile from texacana
in them old cotton fields back home



\song{all the good times}{}

i wish to the lord i'd never been born
or died when i was young
and never had seen you sparkling blue eyes
or where you light did shine

\R all the good times are past and gone
   all the good times are o'er
   all the good times are past and gone
   little darling don't you weep for me **

come back, come back my own true love
and stay a while with me
for if ever i had a friend in this world
you've been a friend to me \s

don't you see that distant train
come whiriling around the bend
it's taking me away from this old town
to never return again \s

i wish to the lord i'd never been born
or died when i was young
i never would have seen your sparkling blue eyes
or heard your lying tongue \s

see that lonesome turtle dove
come flying from pine to pine
he's mournin'  for his own true love
just like i mourn for mine \s

come back, come back my own true love
and stay a while with me
for if ever i had a friend in this world
you've been a friend to me



\song{amazing grace}{}

a/F mazing /F7 grace, how /B sweet the /F sound
that saved a /a wretch like /C me
i /F once was /F7 lost but /B now i'm /F found
was /d blind but /C now i /F see \S

'twas grace that taught my heart to fear
and grace my fear relieved
how precious did that grace appear
the hour i first believed \s

when we've been there ten thousand years
bright shining as the sun
we've no less day to sing god's price
than when we first begun \s

through many dangers, toils and snares
i have already come
'tis grace hath brought me safe thus far
and grace will lead me home \s

amazing grace, how sweet the sound
that saved a wretch like me
i once was lost but now i'm found
was blind but now i see



\Song{irene, good night}{}

{\i chorus: }
irene, good night, irene, good night
good night irene good night irene
i'll kiss you in my dreams \s

sometimes i live in the country
sometimes i live in town
sometimes i take a great notion
to jump in the river and drown



\song{country roads}{}

/G almost heaven /e west virginia
/D blue ridge mountains
/C shenandoah /G river
/G life is older, /e older than the trees
/D younger that the mountains
/C blowing like a /G breeze \S

all my memories, get her round here
my is lady
stranger to blue water
dark and dusty painted on the ksy
missed the taste of moonshine
teardrops in my eyes

\R country /G roads, take me /D home
   to the /e place i bel/C ong
   west vir/G ginia, mountain /D mamma
   take me /C home country /G roads **

{\i interplay:} \s
/G i hear her /D voice in the /G morning how she calls me
/C radio re/G mindes me off my /a home /e far a/D way
/e driving down the /D road i get this /G feeling that i /e should
be home /D yesterday, yester/D7 day \S

\r country roads...



\song{de gospel train}{}

de /G gospel train's a/e comin'
i /C hear it just at h/D an'
i h/G ear de car-wheels /e rumblin'
an' r/G ollin' t/D hro' de l/G an'

\R  den git on bo/C ard, little children
    git on bo/G ard, little children
    git on bo/C ard, little chil/A7 dren
    dere's /G room for /D many an' /G mo' **


i hear de train acomin'
she's comin' roun' de curve
she's loosend all her stream and brakes
an' strainin' ev'ry nerve

\r den git...

de fare is cheap an' all can go
de rich an' poor are dere
no second class aboard dis train
no diff'rence i de fare

\r den git...



\song{dixie land}{}

i /C wish i was in the land of cotton
/F old times there are not forgotten
look a/C way! look away! look a/G way! dixie /C land
in /C dixie land where i was born in
/F early on one frosty morning
look a/C way! look away! look a/G way! dixie /C land

\R  then i /C wish i was in /F dixie hoo/G ray! hooray!
    in /C dixie land i'll /F take my stand
    to /C live and die in /G dixie
    a/C way, a/G way, a/C way, down south in /{(G C)} dixie
    a/C way, a/G way, a/C way, down south in /{(G C)} dixie **


old missus marry will ``de weaver''
willium was a gay deceiver
look away! look away! look away! dixie land!
but when he put his arm around her
he smil'd as fierce as forty pounder
look away! look away! look away! dixie land! \s

his face was sharp as a butcher's cleaver
but dad did not seem to grieve her
look away! look away! look away! dixie land!
old missus acted the foolish part
and died for a man that broke heart
look away! look away! look away! dixie land



\song{green fields}{}

/a once there were /d green fields /a kissed by the /E sun
/a once there were /G valleys where /C rivers used to /G run
/F once there were /G blue skies /C white clouds high a/a bove
/d once they were /G part on an /C ever-lasting /E love
/a we were the /d lovers who /a strode /E through green fields \S

green fields are gone now, parched by the sun
gone from the valleys where rivers used to run
gone with the cold wind that swept into my heart
gone with tho lovers who let their dreams depart
where are the green fields that we used to know

\R  /F i'll never know what /G made you run a/C way
    /F how can i keep searching when /G dark clouds hide the /{C E} day
    /a i only know there's nothing here for /d me
    /a nothing in this /d wide world /G left for me to /E see **

but i'll keep on waitig till you return
i'll keep on waiting until the day you learn:
you can't be happy while your heart is on the moam
home to the green fields and me, once again



\song{home on the range}{}

oh, /G give me a home where the /C buffalo roam
where the /G deer and the antelope /D play
where /G seldom is /G7 heard a dis/C couraging word
and the /G skies are not /D cloudy all /G day. \S

\R  /D home, home on the /G range
    where the /e deer and the /a antelope /D play
    where /G seldom is /G7 heard a dis/C couraging word
    and the /G skies are not /D cloudy all /G day. **

oh, give me a land where the bright diamond sand
flows leisurely down the stream
where the graceful white swan goes gliding along
like a maid in a heavenly dream \s

where the air si so pure, the zephyrs so free
the breezes so balmy and light
that i would not exchange my home on the range
for all the cities so bright \s

how often at night when the heavens are bright
with the light from the glittering stars
i have stood there amazed and asked as i gazed
if their glory exceeds that of ours \s

oh, i love those wold flowers in the dear land of ours
the curlew i love to hear scream
and i love those white rocks and the antelope flocks
that graze on the mountain tops green \s



\song{john brown's body}{}

/G john brown's body lies a-/G7 mould'ring in the grave
/C john brown's body lies a-/G mould'ring in the grave
john brown's body lies a-/H7 mould'ring in the /e grave
but his /a soul goes /D marching /G on \S


\R  glory, glory, hallelujah
    glory, glory, hallelujah
    glory, glory, hallelujah
    but his soul goes marchnig on  \qquad (or other) **

\[ he captured harper's ferry with his nineteen men so true \]
and frightened old virginia till she trembled through an through \s

\[ they hanged him for a traitor, themselves the traitor crew \]
but his soul goes marching on \s

\[ john brown died that the slave might be free \]
but his soul goes marching on \s

\[ the stars above in heaven now are looking kindly down \]
on the grave of old john brown \s

\[ he's gone to be a soldier in the army of the lord \]
but his soul goes marching on \s



\song{joshua fit de battle ob jerico}{}

/d joshua fit de battle ob /F jerico, /g jerico, /A7 jerico
/d joshua fit de battle ob /F jerico
an' de /g walls come /a tumblin' /d down \S

you may /d talk about yo' king ob /F gideon
you may /g talk about yo' man ob /A saul
dere's /d none like good ale /F joshua
at de /g battle ob /A jeri/d co \S

up to de walls ob jerico
he marchard with spear in han'
``go blow dem ram horns'' joshua cried
``kase de battle am in my han'.'' \s

den de lam ram sheep horns begin to blow
trumpets begin to soun'
joshua commanded de chillen to shout
an' de walls come tumblin' down.  \qquad	dat morning \s

joshua fit de battle ob jerico, jerico, jerico
joshua fit de battle ob jerico
an' de walls come tumblin' down
an' de walls come tumblin' down
an' de walls come tumblin' down



\song{marching thro' georgia}{}

/G bring the good old bugle, boys, we'll /C sing another /G song
sing it with a /e spirit that will /a start the world a/D long!
/G sing it as we /C us'd to sing it /G fifty thousand /e strong
/a while we were /D marching thro' /G georgia

\R  hur/G rah! hurrah! we /C bring the jubi/G lee!
    hurrah! hurrah! the /a flag that makes you /D free!
    /G so we sang the /C chorus from /G atlanta to the /e sea!
    /a while we were /D marching thro' /G georgia. **


how the darkies shouted when they heard the joyful sound
how the turkey gobbled which our commissary found
how the sweet potatoes even started from the ground
while we were marching thro' georgia \s

yes, and there were ``union'' men who wept with joyful tears
when they saw the honour'd flag they had no seen for years
hardly could they be restrained from breaking forth in cheers
while we were marching thro' georgia \s

``sherman's dashing yankee lads will never reach the coast''
so the saucy rebels said, and 'twas a handsome boast
had they not forgot, alas, to reckon with the host
while we were marching thro' georgia \s

so we made a thoroughfare for freedom and her train
sixty miles in latitude, three hundred to the main
treason fled before us for resistance was in vain
while we were marching thro' georgia



\song{my old kentucky home}{}

the /G sun shines bright in the /C old kentucky /G home
'tis summer, the darkies are /D gay
the /G cornstop's ripe and the /C meadow's in the /G bloom
while the birds make /D music all the /G day \S

the young folks roll on the little cabin floor
all merry, all happy and bright
by'n bye hard times come aknocking at the door
then my old kentucky home, good night

\R  /G weep no /C more, my /G lady
    o weep no /A7 more to/D day
    we will /G sing one song for the /C old kentucky /G home
    for the old kentucky /D home, far a/G way. **

they hunt no more for the 'possum and the coon
on the meadow, the hill and the shore
they sing no more by the glimmer of the moon
on the bench by the old cabin floor \s

the day goes by like a shadow o'er the heart
with sorrow where allways delight
the time has come when the darkies have to part
then my old kentucky home, good night \S


the head must bow and the back will have to bend
wherever the darky may go
A few more days and the trouble all will end
in the field where the sugarcanes grow \s

A few more days for to tote the weary load
no matter 'twill never be light
A few more days till we totter on the road
then my old kentucky home, good night



\song{nine-pound hammer}{}

this nine-pound /G hammer
is a little too /C heavy
for my /G size
/D honey, for my /{G D} size

\R  roll on, /G buddy
    don't you roll so /C slow
    buddy, how can i /G roll
    /D when the wheels won't /{G D} go **

i'm going on the mountain
just to see my baby
and i ain't coming back
no i ain't coming back \s

this nine-pound hammer
it killed john henry
but it can't kill me
buddy, no it can't kill me \s

it's a long way to harlan
and a long way to hazard
just to get a little booze
just to get a little booze \s

there ain't one hammer
down in this tunel
that can ring like mine
that can ring like mine

\R  rings like silver
shines like gold
rings like silver, rings like silver
shines like gold. **

\r  roll on...



\song{oh, freedom}{}

oh, freedom, oh freedom, oh freedom over me
before i'd be a slave i'd be buried in my grave
and go home to my lord and be free \S

no more weeping, no more weeping... \s

no more crying, no more crying... \s

there'll be singing, ther'll be singing...



\Song{oh, susanna}{}

i've /D come from alabama with my banjo on my /A knee
i'm /D going to louisiana my true love /A for to /D see
it /D rained all night the day i left the weather was so /A dry
the /D sun so hot i froze to death, susanna, /A don't you /D cry

\R  /G oh, susanna, oh, /D don't you cry for /A me
    i've /D come from alabama with my banjo /A on my /D knee. **

i had a dream the other night when everything was still
i thought i saw susanna dear a-coming down the hill
the red, red rose was in her hand the tear was in her eye
i said: ``i'm coming from the south, susanna don't you cry.'' \s

i soon will be in new orleans and then i'll look all 'round
and when i find susanna, i'll fall upon the ground
but if i do not find her, then i'll surely die
and when i'm dead and buried, susanna don't you cry



\song{sailing}{}

/E i am sailing, i am /cis sailing
home a/A gain, 'cross the /E sea 
i am /fis sailing stromy /cis waters
to be /fis near you /H7 to be /{E H7} free \S

i am flying, i am flying
like a bird 'cross the sky
i am flying, passing high clouds
to be near you, to be free \s

can you hear me, can you hear me?
through the dark night, far away
i am crying, forever dying
to be near you, who can say? \s

we are sailing, we are sailing
home again, 'cross the sea
we are sailing stromy waters
to be near you, to be free \s

oh lord, to be near you, to be free
oh my lord, to be near you, to be free
oh lord, to be near you, to be free



\song{scarborough fair}{}

/d are you going to /C scarborough /d fair? 
/F parsley /d sage, rosema/G ry and /d thyme
remember /F me to one who lives /C there
/d she once /G was /{B C} a true love of /d mine \S

nebo:
/d are you going to /C scarborough /d fair? 
/F parsley /d sage, rosemary and thyme
remember /F me to one /e who /d lives /C there
/d she once /C was /d a /C true /d love /C of /d mine \S

tell her to make me a cambric shirt
--- on the side of a hill in the deep forest green
parsley sage rosemary and thyme
--- tracing a sparrow on snow-crested brown
without no seams nor needle work
--- blankets and bedclothes the child of the mountains
then she'll be a true love of mine
--- sleeps unaware of the clarion call \S

tell her to find me an acre of land
--- on the side of a hill, a sprinkling of leaves
parsley sage rosemary and thyme
--- washes the grave with silvery tears
between the salt water and the sea strands
--- a soldier cleans and polishes a gun
then she'll be a true love of mine \S

tell her to reap it with a sickle of leather
--- war bellows blazing in scarlet battalions
parsley sage rosemary and thyme
--- generals order their soldiers to kill
and gather it all in a bunch of heather
--- and to fight for a cause they've long ago forgotten
then she'll be a true love of mine \S

are you going...


\song{the sound of silence}{}

/h hello, darkness, my old /A friend
i've come to talk with you /h again
because a vision softl/G y cree/D ping
left its seeds while i w/G as slee/D ping
and the /G vision that was planted in my /D brain
still re/h mains, /D within the /A sounds of /h silence \S

in restless dreams i walked alone
narrow streets of cobblestone
'neath the halo of a street lamp
i turned my collar to the cold and damp
when my eyes were stabbed by the flash of a neon light
that split the night and touched the sound of silence \s

and in the naked light i saw
ten thousand people maybe more
people talking without speaking
people hearing without listening
people writing songs that voices never shared
and no one dare disturb the sound of silence \s

``fools,'' said i, ``you do not know
silence like a cancer grows.''
``hear my words that i might teach you
take my arms that i might reach you.''
but my words like silent rain-drops fell
and echoed in the wells of silence \s

and the people bowed and prayed
to the neon god they made
and the sign flashed out its warning
in the words that it was forming
and the sign said: ``the words of the prophets are written on \rest{the subway walls}
and tenement halls
and whispered in the sounds of silence.''



\song{swing low, sweet chariot}{}

\R  swing low, sweet chariot
coming for the carry me home
swing low, sweet chariot
coming for the carry me home. **

i looked over jordan and what did i see
coming for the carry me home
A band of angels coming after me
coming for the carry me home \s

if you get there before i do
coming for the carry me home
tell all my friends i'm coming too
coming for the carry me home \s

i'm sometimes up and sometimes down
coming for the carry me home
but still my soul feels heavenly bound
coming for the carry me home



\Song{ten green bottles}{}

/D ten green bottles /A hanging on the /D wall
/D ten green bottles /A hanging on the /D wall
if /G one green /D bottle should /A accidentaly fall
there would be /D nine green bottles /A hanging on the /D wall \S

(nine, eight, ... , no green bottle hanging on the wall)



\song{the cruel war}{}

the /G cruel war is /e raging, /a johnny has to /H fight
oh, i /C want to go /a with him, from /G morning till /D night
i /G want to go /e with him. it /a grieves my heart /H so
won't you /C let me go /a with you? /G no, /C my love, /G no! \S

tomorrow is sunday. monday is the day
that your captain will call you, and you must obey
your captain will call you. it grieves my heart so
won't you let me go with you? no, my love, no! \s

i'll go to your captain and get down upon my knees
ten thousand gold guineas i'll give for your release
ten thousand gold guineas. it grieves my heart so
won't you let me go with you? no, my love, no! \s

your fingers are too slender. your figure is too small
your cheeks are too rosy to face the cannonball
your cheeks are too rosy. it grieves my heart so
please, let me go with you! no, my love, no!



\Song{wayfaring stranger}{}

i'm just a /a poor /(e) wayfaring /a stranger
a-travelling /d through this world of /a woe
and there's no /a sadness, /(e) toil or /a danger
to that bright /d world to /(G) which i /a go

\R  i'm going /F there to meet my /C father
    i'm going /F there no more to /E roam
    i'm just /a a-going /(e) over /a jordan
    i'm just /d a-going /(G) over /a home. **

i know dark clouds will gather 'round me
i know my way is dark and steep
but beautious fields lie just before me
where soul's redeemed that vigils keep

\r  i'm going...



\song{the wabash cannonball}{}

\R  /G listen to the jungle
    to the rumble and the /C roar
    as she /D glides along the woodlands
    through the hills and by the /G shore
    hear the /G mighty rush of engine
    hear the lonesome hoboes /C squall
    while /D travelling through the jungle
    the wabash /G cannonball **

from the great atlantic ocean to the wild pacific shore
from sunny california to the ice-bound labrador
she's mighty tall and handsome, she's known quite well by all
she's boes accomodation on the wabash cannonball \s

this train she runs to memphis, matoon and mexico
she rolls through east st. louis and she never does it slow
as she flies through colorado, she gives an awfull squall
they tell her by her whistle the wabash cannonball \s

our eastern states are dandy, so the people always say
from new york to st. louis and chicago by the way
from the hills of minnesota where the rippling water fall
no changes can be taken on the wabash cannonball \s

now here's the boston blackey, may his name forever stand
and long to be remembered by the bums throughout the land
his earthly days are over and the curtains round him fall
we'll carry him home to victory on the wabash cannonball



\song{there is a tavern in the town}{}

there is a tavern in the town, in the town
and there my dear love sits him down, sits him down
and drinks his wine 'mid langhter free
and never, never thinks of me

\R  fare thee well for i must leave thee
    do not let the parting grieve thee
    and remember that the best of friend must part, must part
    adieu kind friends, adieu, adieu, adieu, adieu
    i can no longer stay with you, stay with you
    sl'll hang my harp on a weeping willow tree
    and may the world go well with thee. **

he left me for a damsel dark
each friday night they used to spark
and now my love, once true to me
takes that dark damsel on his knee \s

oh! dig my grave both wide and deep
put tombstones at my head and feet
and on my breast carve a turtle-dove
to signify i died of love



\song{tipperary}{}

up to mighty london came an irishman one day
as the streets are paved with gold sure ev'ry one was gay
singing songs of piccadilly, strand and leicester square
till paddy got excited, then he shouted to them there:

\R  it's a /F long way /C to tippe/F rary
    it's a /B long way to /F go
    it's a /F long way /C to little /F mary
    to the /G sweetest girl i /{C C7} know!
    /F goodbye, /C picca/F dilly
    /B farewell, leicester /A square
    it's a /F long, long /G way to tippe/{B F} rary
    but /G my heart's /C right /F there! **

paddy wrote a letter to his irish molly o'
saying ``should you nor receive it, write and let me know!''
``if i make mistakes in `spelling`, molly dear,'' said he
``remember it's the pen that's bad, don't lay the blame on me.'' \s

molly wrote a neat reply to irish paddy o'
saying ``mike maloney wants to marry me, and so
leave the strand and piccadilly, or you'll be to blame
for love has fairly drove me silly-hoping you're the same!''



\song{waltzing matilda}{}

once a jolly swagman camped by a billabong
under the shade of a coolibah tree
and he sang as he watched and waited till his billy boiled:
``you'll come a-waltzing, matilda, with me!''

\R  waltzing matilda, waltzing matilda
    you'll come a-waltzing matilda with me
    and he sang as he watched and waited till his billy boiled:
    ``you'll come a-waltzing, matilda, with me!'' **

down came a jumbuck to drink at that billabong
up jumped the swagman and grabbed him with glee
and he sang as he stowed that jumbuck in his tucker-bag:
``you'll come a waltzing, matilda, with me!''

\R  waltzing matilda, waltzing matilda
    you'll come a-waltzing matilda with me
    and he sang as he stowed that jumbuck in his tucker-bag:
    ``you'll come a-waltzing, matilda, with me!'' **

up rode the squatter, mounted on his thoroughbred
up rode the troopers -- one -- two -- three:
``where's that jolly jumbuck you've got in your tucker-bag?
you'll come a-waltzing, matilda, with me!''

\R  waltzing matilda, waltzing matilda
    you'll come a-waltzing matilda, with me
    ``where's that jolly jumbuck you've got in you tucker-bag?
    you'll come a-waltzing, matilda, with me!'' **

up jumped the swagman and sprang into the billabong
``you'll never catch me alive!'' said he
and his ghost may be heard as you pass by that billabong
``you'll come a-waltzing, matilda, with me!''

\R  waltzing matilda, waltzing matilda
    you'll come a-waltzing matilda with me
    and his ghost may be heard as you pass by that billabong
    ``you'll come a-waltzing, matilda, with me!'' **



\song{we shall overcome}{}

we shall overcome, we shall overcome
we shall overcome some day
oh, deep in my heart, i do believe
we shall overcome some day \S

we'll walk hand in hand...
we shall live in peace...
the whole wide world around...
all men shall be free...
we are not afraid...
we are not alone...
truth will make us free...
the lord will se us through...
we shall brothers be...



\Song{what shall we do with the drunken sailor}{}

/F what shall we /A do with the /d drunken sailor?
/C what shall we /G do with the /C drunken sailor?
/F what shall we /A do with the /E drunken sailor?
/C early /A in the /d morning?

\R  hooray and up she rises
    hooray and up she rises
    hooray and up she rises
    early in the morning **

put him in the longboat until he's sober... \s

pull out the plug and wet him all over... \s

put him in the scuppers with a hose-pipe on him...



\song{yankee doodle}{}

fath'r and i went down to camp, along with captain good'in
and there we saw the men and boys as thick as hasty puddin'

\R  yankee doodle keep it up, yankee doodle dandy
    mind the music and the step and with the girls be handy **

and there we see a thousand men as rich as sguire david
and what they wassted ev'ry day, i wish it could be saved \s

and there was captain washington upon a slapping stallion
a-giving orders to his men; i guess there was a million \s

and then the feathers on his hat they looked so very fine
ah! i wanted peskily to get, to give to my jemima



\Song{brighton inthe rain}{}

i've never been to athens and i've never been to rome
i've only seen the pyramids in picture books at home
i've never sailed across the sea or been inside a plane
i've always spent my holidays in brighton in the rain \s

i've never eaten foreign food or drunk in a foreign bar
i've never  kissed a foreign girl or driven a foreign car
i've never had to find my way in a country i don't know
i've always known just where i am and where i'll never go \s

i've read travel books by writers who have been to pakistan
i've heard people telling stories of adventures in iran
i've watched tv documentaries about china and brazil
but i've never been abroad myself; it's making me feel ill \s

i've studied several languages like Hindi and malay
i've learnt lots of useful sentences i've never been able to say
the furthest place i've ever been was to the isle of  man
and that was full of tourists from jamaica and japan \s

i've never been to athens and i've never been to rome
i've only seen the pyramids in picture books at home
i've never sailed across the sea or been inside a plane
i've always spent my holiday in brighton in the rain



\song{leaving on a jet plane}{}

all my /D bags are packed, i'm /G ready to go
i'm /D standing here out/G side your door
i /D hate to wake you /h up to say good/e bye \s

the dawn is breaking, it's early morn
the taxi's waiting, he's blowing his horn
already i'm so lonesome i could cry:

\R  so kiss me and smile for me
    tell me that you'll wait for me
    hold me like you'll never let me go
    i'm leaving on a jet plane
    don't know when i'll be back again
    oh babe i hate to go **

there are so many time i've let you down
so many times i've played around
i tell you now that they don't mean a thing
every place i go i think of you
every song i sing i sing for you
when i come back i'll wear your wedding ring \s

now the time has come to leave you
one more time let me kiss you
then hold me close and i'll be on my way
dream about the days to come
when i won't have to leave alone
about the time when  won't have to say



\song{i'm a little dinosaur}{}

one, two, one, two, three, four, well

i'm a little dinosaur, i'm a little dinosaur
i'm a little dinosaur, but i'm planning to go away
no i am real old, don't you know
born 10 billion years ago
but they don't love me here enough and so
i'm planning to go away
now the children upon their lawn
will wake up and wonder where i've gone
and the flies that buzz around where i now be
they are gonna have to get along without me \s

they'll say ``where's that little dinosaur
where's that little dinosaur
where's that little dinosaur
he must have gone away \s

\[ oh, no, please don't go, oh, no please don't go
don't go little dinosaur, please don't go away. \] \s

hello! o.k.! i'll come back, you know i'm back to stay
because i'm just your little dinosaur
and i could never really go
never really go, never really go away



\song{s.o.s.}{}

/d where are those happy /A days, they seem so hard to /d find
/d i tried to reach for /A you, but you have closed your /d mind
/F whatever happened /C to our love? /g i wish i under/d stood
/d it used to be so /A nice, it used to be so /{d C F C F B F C} good

\R  /F so when you're /C near me
    /g darling can't you /B hear me /{F B F B} s.o.s
    /F the love you /C gave me
    /g nothing else can /B save me /{F B F} s.o.s
    when you're /B gone
    how can /Cis i even /Dis try to go /F on?
    when you're /B gone
    though i /Cis try how can /Dis i carry /F on? **

you seem so far away though you are standing near
you made me feel alive, but something died i fear
i really tried to make it out i wish i understood
what happened to our love, it used to be so good

\r  so when...



\song{mamma mia}{}

i've been cheated by you since i don't know when
so i made up my mind, it must come to an end
look at me now, will i ever learn?
i don't know how but i suddenly lose control
there's a fire within my soul
just one look and i can hear a bell ring
one more look and i forget everyting, o--o--o--oh

\R  mamma mia, here i go again
    my my, how can i resist you?
    mamma mia, does it show again?
    my my, just how much i've missed you
    yes, i've been broken hearted
    blue since the dau we parted
    whe, why did i ever let you go
    mamma mia, now i really know
    my my, i could never le you go **

i've been angry and sad about the things that you do
i can't count all the times that i've told you we're through
and when you go, when you slam the door
i think you know, that you won't be away too long
you know that i'm not that strong
just one look and i can hear a bell ring
one more look and i forget everything, o--o--o--oh

\R  mamma mia, here i go again
my my, how can i resist you?
mamma mia, dows it show again?
my mym, just how much i've missed you
yes, i've been brokenhearted
blues since the day we parted
whe, why did i ever leat you go?
mamma mia, even if i say
bye bye, leave me now or never
mamma mia, it's a game we play
bye bye doesn't mean forever **

\r  mamma mia...



\song{lemon tree}{}

i'm /a sitting here in a /e boring room
that's /a just another rainy sunday /e afternoon
i'm /a wasting my time i've got /e nothing to do
i'm /a hanging around, i'm /e waiting for you
but /d nothing ever happe/e ns, and i /a wonder \S

i'm driving around in my car
i'm driving too fast, i'm driving too far
i'd like to change my point of view
i feel so lonely, i'm waiting for you
but nothing ever happens, and i wonder

\R  i /C wonder how, i /G wonder why
    /a yesterday you told me 'bout the blue, /e blue sky
    and /F all that i can /G see is just the yellow /C lemon tre/G e
    i'm /C turning my head /G up and down
    i'm /a turning, turning, turning, turning, /e turning around
    and /F all that i can /D7 see is just another /G lemon tree **

sing: ta, tadadada... \s

i'm sitting here i miss the power
i'd like to go out taking a shower
but there's a heavy cloud inside my head
i feel so tired put myself into bed
well nothing ever happens and i wonder \s

/E isolation /a is not good for me
/G isolation /C i don't /G want /C to /E sit on the lemon tree \s

i'm stepping around in a desert of joy
baby and he how will get another toy
and everything will happen and you wonder


\songgg{}

\R  i wonder how, i wonder why
    yesterday you told me 'bout the blue, blue sky
    and all that i can see is just another lemon tree
    i'm turning my head up and down
    i'm turning, turning, turning, turning, turning around
    and all that i can see is just the yellow lemon tree \s

    yeah i wonder, wonder \s

    i wonder how, i wonder why
    yesterday you told me 'bout the blue, blue sky
    \[ and all that i can see \] \krat3
    is just the yellow lemon tree **



\Song{i'd rather}{}

i'd /e rather be a sparrow than a /G snail
/C yes, i /G would /C if i /G could i'd /H7 surely /e would /H7 mm /e mm \S

i'd rather be a hammer than a nail
yes i would if i only could i'd surely would mm mm

\R  to/C day i'd rather sail away like a /G swan
    / that's here and gone
    a /C man gets tied up to the throng
    he gives the /G world its saddest song
    its /H7 saddest /e song **

i'd rather be a forest than a street
yes i would if i could i'd surely would \s

i'd rather feel the earth beneath my feet
yes i would if i only could, i'd surely would

\r  today...



\song{yellow submarine}{}

/D in the /A town where /G i was /D born
/h lived a /e man who /G sailed to /A sea
/D and he /A told us /G of his /D life
/h in the /e land of /G subma/A rines \S

so we sailed up to the sun
till we found the sea of gree
and we lived beneath the waves
in our yellow submarine

\R  /D we all live in a /A yellow submarine
    yellow submarine, /D yellow submarine
    /D we all live in a /A yellow submarine
    yellow submarine, /D yellow submarine **

and our friends are all on board
many more of them live next door
and the band begins to play

\r we all...

as we live a life of ease
ev'ry one of us has all we need
sky of blue and sea of green
in our yellow submarine

\rr



\song{i am a rock}{}

a winter's /C day
in a /F deep and dark de/C cember
/d i a/G m a/F lo/C ne
/d gazing from my /e window
/F to the streets be/G low
on a /d freshly fallen /F silent shroud of /G snow

\R /F i am a /C rock
   /F i am an /G isl/a and **

i've built walls
a fortress deep and mighty
that none may penetrate
i have no need for friendship
friendship causes pain
it's laughter and it's loving i disdain

\r i am...

don't talk of love
well, i've heard the word before
it's sleeping in my memory
i won't disturb the slumber
of feelings that have died
if i'd never loved
i never would have cried

\rr

i have my books
and my poetry to protect me
i am shielded in my armor
hiding in my room
safe within my womb
i touch no-one and no-one touches me

\rr

and the /d rock /G feels no /C pain
and an /d island /G never /C cries



\song{mrs. robinson}{}

\R	and here's to /G you mrs. /e robinson
	/G jesus loves you /e more than you will /C know wo wo /D7 wo
	god bless you /G please mrs. /e robinson
	/G heaven holds a /e place for those who /C pray
	hey hey /a hey hey hey /E hey **

we'd /E7 like to know a little bit about you for our files
we'd /A7 like to help you learn to help your/A9 self
/D7 look around you /G all you see are /C sympathetic /a eyes
/E stroll around the grounds un/D7 til you feel at home \S

\r and here's...

hide it in a hiding-place where no one ever goes
put it in your pantry with your cupcakes
it's a little secret just the robinson's affair
most of all you've got to hide it from the kids.

\R	coo coo cachoo mrs. robinson
	jesus loves you more than you will know wo wo wo
	god bless you please mrs. robinson
	heaven holds a place for those who pray
	hey hey hey hey hey hey **

sittting on a sofa on a sunday afternoon
going to the candidates' debate
laugh about it shout about it when you've got to choose
ev'ry way you look at it you lose

\R	where have you gone joe dimaggio
	a nation turns its lonely eyes to you woo woo woo
	what's that you say mrs. robinson
	``joltin' joe'' has left and gone away
	hey hey hey hey hey hey **



\song{bottle of wine}{}

\R  /C bottle of wine, fruit of the vine
    when you gonna let me get /G so/C ber?
    / leave me alone, let me go home
    let me go back and start /G ov/C er **

ramblin' /G round this /F dirty old /C town
singin' for  /G nickles an'  /C dimes
times getting'  /G tough, i /F ain't got en/C ough
to buy a little /G bottle of /C wine \S

\r bottle...

little hotel, older than hell
dark as the coal in the mine
blankets are thin, i lie there and grin
i got a little bottle of wine

\rr

pain in my head and bugs in my bed
pants are so old that they shine
out on the street tell the people i meet
won't you buy me a little bottle of wine 

\rr

well, a preacher will preach and a teacher will teach
a miner will dig in the mine:
i ride the roads, trusting in god
a-huggin' my bottle of wine



\song{wish you were here}{}

\R  /e wish you were here
    me, oh /C my country/D man, wish you were /{G H} here
    /e wish you were here
    don't you /C know the stove is /D getting colder
    /G and i miss you like /H7 hell and i'm feeling /e blue **

/E i've got feelings for /a you, babe
/D do you still feel the /{G H} same?
/E from the first time i /a laid my eyes on you
/D i felt joy of living
i saw /G heaven in your /H7 eye, in your /e eyes \S

\r  wish...

i /a miss your laugh, i miss your smile
i miss /e everything about you
every /a second's like a minute, every /H7 minute's like a day
when you're far a/e way \S

/a wish you were here
the /F stove is gettin' /G colder, baby
/a wish you were here
a /F battlefield of /G love and fear
and /C i wish you were /e here
/C i've got /E feelings for /a you, babe
/F from the /G first time i /a laid my eyes on you \S

\rr



\song{can't help falling in love}{}

/F wise /a men /d say only /B fools /F rush /C in
but /{B C7} i can't /d help /g falling in /F love /C with /F you \S

shall i stay would it be a sin?
if i can't help falling in love with you \s

/a like the river /E7 flows
/a surely to the /E7 sea
/a darling so it /E7 goes
/a some things /D7 are meant to /{g C7} be \S

take my hand, take my whole life too
for i can't help falling in love with you \s

like the river flows
surely to the sea
darling so it goes
some things are meant to be \s

take my hand, take my whole life too
for i can't help falling in love with you
for i can't help falling in love with you


\song{don't stop me now}

to/F night, i'm gonna have my/a self a real /d good time i feel a/g liv/C e
and the /F world, /F7 turning inside /B out, yeah
and /g7 floating around in /D7 ecstasy
so /g don't /F stop /C me /g now, /g don't st/F op /C me
'cause i'm /g7 having a good time, /C having a good time \S

i'm a /F shooting star leaping through the /a sky, like a /d tiger
defying the /g laws of gravi/C ty
i'm a /F racing car, passing /a by, like lady go/d diva
i'm gonna /g go, go, go, /C there's no stopping /F me
i'm /F7 burning through the /B sky, yeah, 2/g7 00 degrees,
that's why they /D7 call me mister fahren/g heit
i'm /D7 travelling at the speed of /g light.
i wanna make a /B super/F sonic /B man out /g7 of yo/C u \S

/F don't /g stop /a me /d now, i'm having such a go/g7 od time
i'm /C having a ball
/F don't /g stop /a me /d now, if you wanna have a go/g7 od time
/D7 just give me a call
/g don't /F stop /C me cause i'm /g7 having a good time
/g don't /F stop /C me, yes i'm /g having a good time
/C i don't want to stop /{b7sus4 (x13141)} at all \songgg


i'm a rocket ship, on my way to mars, on a collision course
i am a satellite, i'm out of control
i'm a sexmachine, ready to reload, like an atombomb
about to oh, oh, oh, oh, to explode
i'm burning through ...n.c. \s

don't stop me, don't stop me, don't stop me, hey hey hey
don't stop me, don't stop me, oh oh oh
don't stop me, don't stop me, have a good time, good time
don't stop me, don't stop me, ahhhhh \s

(guitar)  =  verse

i'm burning through ...
don't stop me now ...



\konec{contents}{in alphabetic order}
\bye




\song{silent night}{}

/A silent night, holy night
/E all is calm, /A all is bright
/D round yon virgin /A mother and child
/D holy infant so /A tender and mild
/E sleep in heavenly /A peace
sleep in /E heavenly /A peace \S

silent night, holy night
shepherds quake at the sight
glories stream from heaven afar
heav'nly hosts sing ``alleluia!''
\[ christ, the savior, is born! \] \s

silent night, holy night
son of god, love's pure light
radiant beams from thy holy face
with the dawn of redeeming grace
\[ jesus, lord, at thy birth! \]



